Robust calibration of numerical models based on relative regret

### 2020-01-27 article.tex
rename figures
back to preprint formatting
corresponding author
ordre auteurs et affiliation

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
\usepackage{jcomp}
\usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\verso{Victor Trappler \textit{etal}}

@@

\author[1]{Victor \snm{Trappler}\corref{cor1}}
\cortext[cor1]{Corresponding author% : 
  % Tel.: +0-000-000-0000;  
  % fax: +0-000-000-0000
  % ;
}
\ead{victor.trappler@univ-grenoble-alpes.fr}
\author[1]{Élise \snm{Arnaud}}
% \fntext[fn1]{This is author footnote for second author.}  
\author[2]{Arthur \snm{Vidard}}
%% Third author's email
% \ead{author3@author.com}
\author[2]{Laurent \snm{Debreu}}

\address[1]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
\fntext[fn1]{Institute of Engineering Univ. Grenoble Alpes}
\address[2]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
\received{}
\finalform{}
\accepted{}
\availableonline{}
\communicated{}

@@

% \begin{keyword}
% %% keywords here, in the form: keyword \sep keyword
% Calibration \sep Robust optimisation \sep Relative-regret \sep shallow-water equations
% %% PACS codes here, in the form: \PACS code \sep code

% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)

% \end{keyword}

@@

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_moments_noscale.pdf}
  \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$. Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are not displayed). Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.}
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}. The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines. 
\begin{figure}[!h]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $\JBH$ along with conditional minimisers in red. Bottom left: Estimated densities using KDE and EM algorithm and the histogram. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $\JBHS$.}
\label{fig:contours}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/relaxation_tuto.pdf}
\caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$. Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red. On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{U}=\mathbf{u})\}$ is in yellow. On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
\label{fig:relax_tuto}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width = \singlecolumnsize]{Figures/illu_alpha_p.pdf}
\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
\label{fig:illu_alpha_p}
\end{figure}

@@

\begin{figure*}[!ht]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $\JBH$ and $\JBHS$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

 \begin{figure}[!ht]
   \centering
\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/profile_BH.pdf}
\caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The profiles of $\kest_{\mathrm{MPE}}$ and $\kest_{\mathrm{ratio}}$ coincide in this case}
\label{fig:profiles_branin}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/profile_BHs.pdf}
\caption{Profiles of the different estimates for $\JBHS$. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\singlecolumnsize]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{U}=\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/alpha_SWE}
  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
\label{fig:alpha_p_SWE}
\end{figure}

@@

Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/profile_swe}
  \caption{Profiles for the calibration problem, for the shallow water case}
\label{fig:profiles_swe}
\end{figure}

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/L2_full_rel.pdf}
\caption{Squared forecast error for the shallow water case, depending on the calibrated parameter. The left figure shows the squared error time-averaged as a function of the spatial coordinate $x$, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_squared_error}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/CRPS_full_rel}
  \caption{CRPS computed for different calibrated parameters for the shallow water case. The left figure shows the CRPS time-averaged as a function of the spatial coordinate $x$, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_crps}
\end{figure}

>>>>

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
% \usepackage{jcomp}
% \usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

% \verso{Victor Trappler \textit{etal}}

@@

\author[1]{Victor {Trappler}\corref{cor1}}
\cortext[cor1]{Corresponding author
  % Tel.: +0-000-000-
  % ;
}
\ead{victor.trappler@univ-grenoble-alpes.fr}
\author[1]{Élise {Arnaud}}
% \fntext[fn1]{This is author footnote for second author.}  
\author[1]{Arthur {Vidard}}
\author[1]{Laurent {Debreu}}

%% Third author's email
% \ead{author3@author.com}

\address[1]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\textsuperscript{1}\fnref{fn1}, LJK, 38000 Grenoble, France}
\fntext[fn1]{Institute of Engineering Univ. Grenoble Alpes}
% \address[2]{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP\fnref{fn1}, LJK, 38000 Grenoble, France}
% \received{}
% \finalform{}
% \accepted{}
% \availableonline{}
% \communicated{}

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Calibration \sep Robust optimisation \sep Relative-regret \sep Shallow-water equations
%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

@@

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/FIG01.pdf}
  \caption{The left column concerns $\JBH$, while the right one deals with $\JBHS$. Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are not displayed). Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line.}
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

Similarly, estimations of $\hatkmpe$ are depicted on Figure~\ref{fig:contours}. The top row shows the contours of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The bottom row presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture, calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines. 
\begin{figure}[!h]
  \centering
  \includegraphics[width=\singlecolumnsize]{Figures/FIG02.pdf}
  \caption{Top Left:  $\JBH$ along with conditional minimisers in red. Bottom left: Estimated densities using KDE and EM algorithm and the histogram. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $\JBHS$.}
\label{fig:contours}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG03.pdf}
\caption{Principle of the relaxation of the constraint on $\JBH$, and illustration of $R_\alpha(\mathbf{k})$. Top plots: Computation of the conditional minimisers $\mathbf{k}^*(\mathbf{u})$. Top right plot: the set $(\mathbf{k}^*(\mathbf{u}),\mathbf{u})$ of conditional minimisers is represented in red. On the bottom left plot, for a relaxation $\alpha=1.5$, and $\mathbf{u}=3$, the acceptable $\mathbf{k}$ are in cyan, while the non-acceptable ones are in orange, while the frontier $\{(\mathbf{k}^*(\mathbf{u}),\mathbf{u}) \mid J^*(\mathbf{u}) = J(\mathbf{k},\mathbf{U}=\mathbf{u})\}$ is in yellow. On the bottom right plot, the set $R_{\alpha}(\mathbf{k})$ for $\alpha=1.5$ and $\mathbf{k}=1.5$ is in green.}
\label{fig:relax_tuto}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width = \singlecolumnsize]{Figures/FIG04.pdf}
\caption{Illustration of the influence of different levels $p$ on $\Gamma_{\alpha_p}$ and on $\mathbf{k}_p$ for $\JBHS$}
\label{fig:illu_alpha_p}
\end{figure}

@@

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/FIG05.pdf}
\caption{Top: $\JBH$ and $\JBHS$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

 \begin{figure}[!ht]
   \centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG06.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBH$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG07.pdf}
\caption{Profiles of the different estimates for $\JBH$, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The profiles of $\kest_{\mathrm{MPE}}$ and $\kest_{\mathrm{ratio}}$ coincide in this case}
\label{fig:profiles_branin}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG08.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for $\JBHS$. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{figure*}[!h]
  \centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG09.pdf}
\caption{Profiles of the different estimates for $\JBHS$. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\singlecolumnsize]{Figures/FIG10.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{U}=\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/FIG11}
  \caption{Evolution of $\alpha_p$ for different levels $p$, and ratio, for the shallow water problem}
\label{fig:alpha_p_SWE}
\end{figure}

@@

Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/FIG12}
  \caption{Profiles for the calibration problem, for the shallow water case}
\label{fig:profiles_swe}
\end{figure}

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=\onehalfcolumn]{Figures/FIG13.pdf}
\caption{Squared forecast error for the shallow water case, depending on the calibrated parameter. The left figure shows the squared error time-averaged as a function of the spatial coordinate $x$, while the right barplot shows the relative change of the mean forecast error, averaged over time and space, taken w.r.t.\ to the best attained performance for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_squared_error}
\end{figure*}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\onehalfcolumn]{Figures/FIG14}
  \caption{CRPS computed for different calibrated parameters for the shallow water case. The left figure shows the CRPS time-averaged as a function of the spatial coordinate $x$, and the right figure shows the relative change of the CRPS averaged over time and space, taken with respect to the best attained CRPS for $\mathbf{k}^*(0.7)$}
\label{fig:forecast_crps}
\end{figure}
